article title

### 2022-07-20 article.tex
Tidy section, subsection lables

\newpage
\section{Introduction}
\label{sec:introduction}
\renewcommand{\epigraphflush}{flushleft}
\renewcommand{\textflush}{flushleft}
\renewcommand{\sourceflush}{flushleft}
\epigraph{Remember, the objective is to take the right action on the process. No
credit is given for finding the `right numbers.'}{Donald J. Wheeler}

@@

\section{Prior research}
\label{sec:prior_research}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Results}
\label{sec:results}

@@

\newpage
\section{Bold, italics, and underline}
\label{sec:bold_italics_underline}
Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

\section{URLs}
\label{sec:urls}
Hyperlinks within the document can be easily added. For example, \hyperref[sec:graphics]{see Graphics} and \hyperref[fig:anatomy_of_a_matplotlib_figure]{Anatomy of a matplotlib figure} and \hyperref[def:limit]{Definition of a limit}.

Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.
\section{Lists}
\subsection{Unordered list}
\label{sec:unordered_list}
\begin{itemize}
    \item Illinois
        \begin{itemize} \item Chicago \item Naperville \end{itemize}
    \item Kentucky
        \begin{itemize} \item Lexington \item Louisville \end{itemize}
\end{itemize}

\subsection{Ordered list}
\label{sec:ordered_list}
\begin{enumerate}
    \item Cat
        \begin{enumerate}
            \item Persian
            \item Siamese
        \end{enumerate}
    \item Dog
        \begin{enumerate}
            \item Aussiedoodle
            \item Newfoundland
        \end{enumerate}
\end{enumerate}

\newpage
\section{Graphics}
\label{sec:graphics}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\newpage
\section{Tables}
\label{sec:tables}

\subsection{Simple table}
\label{sec:simple_table}`

@@

\subsection{Multirow table}
\label{sec:multirow_table}`
\begin{table}[H]
\footnotesize
\centering
\begin{tabular}{llll}
\toprule
                                           & \textbf{Process requirement}            & \textbf{Sampling}                        & \textbf{Comments} \\
\midrule
\multirow[t]{4}{*}{$C_\text{pk}$}          & - Stable and predictable variation      & - Rational                               & - Possible cost to increasing $C_\text{pk}$ \\
                                           & - Normal distribution                   & - Representative of process              & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$P_\text{pk}$}          & - Stable and predictable variation      & - Random                                 & - Possible cost to increasing ppk \\
                                           & - Normal distribution                   & - Sufficiently large, representative     & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & - Easiest formulae to explain \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$C_\text{pm}$}          & - Stable and predictable variation      & - Same as $C_\text{pk}$ or $P_\text{pk}$ & - $C_\text{pm}$ penalizes for being off-target \\
                                           & - Normal distribution                   &                                          & - Wide confidence interval \\
                                           & - Need at least one specification limit &                                          & - Most difficult formulae to explain \\
                                           & - Need specification target             &                                          & \\
\bottomrule
\end{tabular}
\caption{Comparison of capability indices}
\label{tab:comparison_capability_indices}
\end{table}

\newpage
\section{Mathematics}
\label{sec:mathematics}

\subsection{Inline mathematics}
\label{sec:inline_mathematics}`
Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.

\subsection{Display-style mathematics}
\label{sec:display_style_mathematics}
Examples of mathematics on their own lines. All equations are flush-left to the page unless multilines, and thus aligned on a symbol with the longest equation flush-left. The equations numbers are flush-right.

@@

\newpage
\section{Greek letters}
\label{sec:greek_letters}

\subsection{Greek Unicode}
\label{sec:greek_unicode}

@@

\newpage
\subsection{Greek mathematics}
\label{sec:greek_mathematics}

@@

\newpage
\subsection{Greek text}
\label{sec:greek_text}

@@

\newpage
\section{Theorems}
\label{sec:theorems}

@@

\section{Definitions}
\label{sec:definitions}

@@

\section{Corollaries}
\label{sec:corollaries}
\begin{corollary}
If $f$ is continuous on the interval $[a,b]$, then \[\int_a^b f(x)dx=F(b)-F(a)\] where $F$ is any antiderivative of $f$.
\end{corollary}
\mycorollaries{f is continuous}

\newpage
\section{Lemmas}

\label{sec:lemmas}
\begin{lemma}
$x+y=z$
\end{lemma}
\mylemmas{Lem 1}

@@

\newpage
\section{Propositions}

\label{sec:propositions}
\begin{proposition}
$x+y=z$
\end{proposition}
\mypropositions{Prop 1}

@@

\newpage
\section{Citations}
\label{sec:citations}

@@

\newpage
\section{Acknowledgements}
\label{sec:acknowledgements}

@@

\section{Supporting information}
\label{sec:supporting_information}

@@

\newpage
\section{References}
\nocite{*}
\printbibliography[heading=none]
\label{sec:references}

>>>>

\newpage
\section{Introduction}\label{sec:introduction}
\renewcommand{\epigraphflush}{flushleft}
\renewcommand{\textflush}{flushleft}
\renewcommand{\sourceflush}{flushleft}
\epigraph{Remember, the objective is to take the right action on the process. No
credit is given for finding the `right numbers.'}{Donald J. Wheeler}

@@

\section{Prior research}\label{sec:prior_research}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\section{Results}\label{sec:results}

@@

\newpage
\section{Bold, italics, and underline}\label{sec:bold_italics_underline}
Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

\section{URLs}\label{sec:urls}
Hyperlinks within the document can be easily added. For example, \hyperref[sec:graphics]{see Graphics} and \hyperref[fig:anatomy_of_a_matplotlib_figure]{Anatomy of a matplotlib figure} and \hyperref[def:limit]{Definition of a limit}.

Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.
\section{Lists}\label{sec:lists}
\subsection{Unordered list}\label{sec:unordered_list}
\begin{itemize}
    \item Illinois
        \begin{itemize} \item Chicago \item Naperville \end{itemize}
    \item Kentucky
        \begin{itemize} \item Lexington \item Louisville \end{itemize}
\end{itemize}

\subsection{Ordered list}\label{sec:ordered_list}
\begin{enumerate}
    \item Cat
        \begin{enumerate}
            \item Persian
            \item Siamese
        \end{enumerate}
    \item Dog
        \begin{enumerate}
            \item Aussiedoodle
            \item Newfoundland
        \end{enumerate}
\end{enumerate}

\newpage
\section{Graphics}\label{sec:graphics}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\newpage
\section{Tables}\label{sec:tables}

\subsection{Simple table}\label{sec:simple_table}`

@@

\subsection{Multirow table}\label{sec:multirow_table}`
\begin{table}[H]
\footnotesize
\centering
\begin{tabular}{llll}
\toprule
                                           & \textbf{Process requirement}            & \textbf{Sampling}                        & \textbf{Comments} \\
\midrule
\multirow[t]{4}{*}{$C_\text{pk}$}          & - Stable and predictable variation      & - Rational                               & - Possible cost to increasing $C_\text{pk}$ \\
                                           & - Normal distribution                   & - Representative of process              & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$P_\text{pk}$}          & - Stable and predictable variation      & - Random                                 & - Possible cost to increasing ppk \\
                                           & - Normal distribution                   & - Sufficiently large, representative     & - Wide confidence interval \\
                                           & - Need at least one specification limit & - Ensure same process conditions         & - Easiest formulae to explain \\
                                           &                                         & - No identifiable condition changes      & \\
\multirow[t]{4}{*}{$C_\text{pm}$}          & - Stable and predictable variation      & - Same as $C_\text{pk}$ or $P_\text{pk}$ & - $C_\text{pm}$ penalizes for being off-target \\
                                           & - Normal distribution                   &                                          & - Wide confidence interval \\
                                           & - Need at least one specification limit &                                          & - Most difficult formulae to explain \\
                                           & - Need specification target             &                                          & \\
\bottomrule
\end{tabular}
\caption{Comparison of capability indices}
\label{tab:comparison_capability_indices}
\end{table}

\newpage
\section{Mathematics}\label{sec:mathematics}

\subsection{Inline mathematics}\label{sec:inline_mathematics}`
Examples of inline mathematics $\frac{a}{b}$, followed by text and another inline equation $\lim_{x\to 0}\frac{\sin x}{x}$=1 and more text $\sum_{k=0}^\infty \frac{1}{2^k}=2$ and finally much more text to cover many lines of a paragraph.

\subsection{Display-style mathematics}\label{sec:display_style_mathematics}
Examples of mathematics on their own lines. All equations are flush-left to the page unless multilines, and thus aligned on a symbol with the longest equation flush-left. The equations numbers are flush-right.

@@

\newpage
\section{Greek letters}\label{sec:greek_letters}

\subsection{Greek Unicode}\label{sec:greek_unicode}

@@

\newpage
\subsection{Greek mathematics}\label{sec:greek_mathematics}

@@

\newpage
\subsection{Greek text}\label{sec:greek_text}

@@

\newpage
\section{Theorems}\label{sec:theorems}

@@

\section{Definitions}\label{sec:definitions}

@@

\section{Corollaries}\label{sec:corollaries}
\begin{corollary}
If $f$ is continuous on the interval $[a,b]$, then \[\int_a^b f(x)dx=F(b)-F(a)\] where $F$ is any antiderivative of $f$.
\end{corollary}
\mycorollaries{f is continuous}

\newpage
\section{Lemmas}\label{sec:lemmas}
\begin{lemma}
$x+y=z$
\end{lemma}
\mylemmas{Lem 1}

@@

\newpage
\section{Propositions}\label{sec:propositions}
\begin{proposition}
$x+y=z$
\end{proposition}
\mypropositions{Prop 1}

@@

\newpage
\section{Citations}\label{sec:citations}

@@

\newpage
\section{Acknowledgements}\label{sec:acknowledgements}

@@

\section{Supporting information}\label{sec:supporting_information}

@@

\newpage
\section{References}\label{sec:references}
\nocite{*}
\printbibliography[heading=none]
